MSHS COVID-19 Vaccinations

### 2021-03-23 Evening-Huddle-Stats.Rmd
Update file paths based on new folder names.

  raw_df <- read.csv(choose.files(
    default =
      paste0(user_directory, "/Epic 340PM Sched All Status/*.*"),
    caption = "Select this afternoon's Epic schedule"),
    stringsAsFactors = FALSE,
    check.names = FALSE)

>>>>

  raw_df <- read.csv(choose.files(
    default =
      paste0(user_directory, "/Epic PM Huddle Sched All Status/*.*"),
    caption = "Select this afternoon's Epic schedule"),
    stringsAsFactors = FALSE,
    check.names = FALSE)
